\section{Question II}
\subsection{Logistic Regression}

\subsubsection{Tuning Learning Rate}
For this experiment, logistic regression was trained with a batch size of 32, L2 regularization set to 0.01, and a learning rate from the range $\{10^{-5}, 10^{-3}, 0.1\}$. The training was conducted for 100 epochs.

\begin{table}[h]
\centering
\caption{Logistic Regression: Tuning Learning Rate}
\label{tab:logistic_regression_lr}
\begin{tabularx}{\columnwidth}{|X|X|X|X|X|}
\hline
\textbf{BS} & \textbf{LR} & \textbf{L2} & \textbf{Val Acc} & \textbf{Test Acc} \\ \hline
 32 & $10^{-5}$ & 0.01 & 0.4694 & 0.4623 \\ \hline
 32 & $10^{-3}$ & 0.01 & 0.5264 & 0.5247 \\ \hline
 32 & 0.1 & 0.01 & 0.3889 & 0.3807 \\ \hline
\end{tabularx}
\end{table}

The best performance was achieved with a learning rate of $10^{-3}$, resulting in the highest validation and test accuracy (\cref{tab:logistic_regression_lr}). The training and validation losses for different learning rates are shown in \cref{fig:log_reg_loss}, and the validation accuracies are presented in \cref{fig:log_reg_acc}.

\subsection{Feedforward Neural Network (MLP)}

\subsubsection{Default Hyperparameters vs. Batch Size = 512}
For this experiment, the default hyperparameters were used, and the batch size was varied between 64 (default) and 512.

\begin{table}[h]
\centering
\caption{Feedforward Neural Network: Default Hyperparameters vs. Batch Size = 512}
\label{tab:mlp_batch_sizes}
\begin{tabularx}{\columnwidth}{|X|X|X|X|X|X|}
\hline
 \textbf{BS} & \textbf{HS} & \textbf{L} & \textbf{Drop} & \textbf{Val Acc} & \textbf{Test Acc} \\ \hline
 64 & 200 & 2 & 0.3 & 0.6068 & 0.6057 \\ \hline
 512 & 200 & 2 & 0.3 & 0.5028 & 0.5200 \\ \hline
\end{tabularx}
\end{table}

The results (\cref{tab:mlp_batch_sizes}) demonstrate that a smaller batch size (64) yields better performance. The corresponding training and validation losses are presented in \cref{fig:mlp_batch_size_loss}, and the validation accuracies are in \cref{fig:mlp_batch_size_acc}.

\subsubsection{Effect of Dropout}
The effect of different dropout values $\{0.01, 0.25, 0.5\}$ was explored.

\begin{table}[h]
\centering
\caption{Feedforward Neural Network: Effect of Dropout}
\label{tab:mlp_dropout}
\begin{tabularx}{\columnwidth}{|X|X|X|X|X|X|}
\hline
\textbf{Model} & \textbf{Drop} & \textbf{HS} & \textbf{L} & \textbf{Val Acc} & \textbf{Test Acc} \\ \hline
MLP & 0.01 & 200 & 2 & 0.5741 & 0.5713 \\ \hline
MLP & 0.25 & 200 & 2 & 0.6054 & 0.6000 \\ \hline
MLP & 0.5 & 200 & 2 & 0.6026 & 0.5963 \\ \hline
\end{tabularx}
\end{table}

The results (\cref{tab:mlp_dropout}) indicate that dropout values around 0.25–0.3 achieve the best balance between regularization and performance. Training and validation losses for different dropout values are shown in \cref{fig:mlp_dropout_loss}, and the validation accuracies are presented in \cref{fig:mlp_dropout_acc}.

\subsubsection{Effect of Momentum}
Momentum values $\{0.0, 0.9\}$ were tested with a batch size of 1024.

\begin{table}[h]
\centering
\caption{Feedforward Neural Network: Effect of Momentum}
\label{tab:mlp_momentum}
\begin{tabularx}{\columnwidth}{|X|X|X|X|X|X|}
\hline
\textbf{Model} & \textbf{Mom} & \textbf{BS} & \textbf{Val Acc} & \textbf{Test Acc} \\ \hline
MLP & 0.0 & 1024 & 0.4701 & 0.4883 \\ \hline
MLP & 0.9 & 1024 & 0.5933 & 0.6033 \\ \hline
\end{tabularx}
\end{table}

The results (\cref{tab:mlp_momentum}) demonstrate that using momentum significantly improves validation and test accuracy. Training and validation losses for different momentum values are shown in \cref{fig:mlp_momentum_loss}, and the validation accuracies are presented in \cref{fig:mlp_momentum_acc}.

\subsection{Discussion}
The results show:
\begin{itemize}
    \item The optimal learning rate for logistic regression was $10^{-3}$ (\cref{tab:logistic_regression_lr}).
    \item Increasing the batch size reduced training time but negatively impacted accuracy (\cref{tab:mlp_batch_sizes}).
    \item Dropout values around 0.25 to 0.3 balanced regularization and model performance (\cref{tab:mlp_dropout}).
    \item Momentum significantly improved accuracy for large batch sizes (\cref{tab:mlp_momentum}).
\end{itemize}